### 2011-11-10 trunk/ipmu2012/preliminaries.tex
A more detailed introduction.

\subsection{Temporal databases}
%In this section, the proposed reasoning is applied to the specific context of intervals on the real line. This setting is of specific interest in the context of fuzzy temporal databases.
A temporal database \cite{Dyreson1994} is a database that manages some aspects of time in its schema. A \textbf{chronon} is the shortest duration of time supported by the database. The time can be represented either as points or intervals \cite{655777}. Fuzzy temporal models \cite{4481150} are proposed when the time points or intervals are not precisely known. There are proposals for the  fuzzyfication of the time point \cite{Dubois89} and the fuzzyfication of the time interval \cite{Garrido2009}.\\
Allen \cite{Allen:1983:MKT:182.358434} studied the comparison between two crisp time intervals. For fuzzy intervals, several proposals \cite{4481150}, \cite{springerlink:10.1007/978-3-540-39964-3_57},\cite{10.1109/TIME.2004.1314418} have been done.

@@

\begin{itemize}
	\item
	\textbf{Transaction time}: The time when the fact is stored in the database.
	\item
	\textbf{Valid time}: The time when the fact is true in the modelled reality.
	\item
	\textbf{Decision time} \cite{Nascimento95decisiontime}: The time when an event was decided to happen. 
	\end{itemize}

	 The  database model can be then classified into: transaction time \cite{Ston87},\cite{Jensen:1991:IIM:627283.627484}, Valid time, bi-temporal \cite{Snodgrass:1984:TQL:588011.588041}(both valid and transaction time) or tri-temporal \cite{Nascimento95decisiontime} (valid, transaction and decision time).

Fuzzy temporal models \cite{4481150} deal with time points \cite{Dubois89} or intervals \cite{Garrido2009} that are ill-known. Some fuzzy temporal models assume that the time stored in the database is an interval. The temporal interval is represented by two ill-known time points: $X$  an ill-known starting point and $Y$ an ill-known ending point. The interval $\left[X,Y\right]$ is not a fuzzy interval but an ill-known interval: it is a crisp interval but it is partially unknown which values are in this interval.

>>>>

\subsection{Temporal databases}
%In this section, the proposed reasoning is applied to the specific context of intervals on the real line. This setting is of specific interest in the context of fuzzy temporal databases.
A temporal database \cite{Dyreson1994} is a database that manages some aspects of time in its schema. A \textbf{chronon} is the shortest duration of time supported by the database. The time can be represented either as points or intervals \cite{655777}. Fuzzy temporal models \cite{schockaert08} are proposed when the time points or intervals are not precisely known. There are proposals for the  fuzzyfication of the time point \cite{Dubois89} and the fuzzyfication of the time interval \cite{Garrido2009}.\\
Allen \cite{Allen83} studied the comparison between two crisp time intervals. For fuzzy intervals, several proposals \cite{ohlbach04,nagypal03,schockaert08} have been done.

@@

\begin{itemize}
	\item
	\textbf{Transaction time}: The time when the fact is stored in the database.
	\item
	\textbf{Valid time}: The time when the fact is true in the modelled reality.
	\item
	\textbf{Decision time} \cite{Nascimento95}: The time when an event was decided to happen. 
	\end{itemize}

	 The  database model can be then classified into: transaction time \cite{Ston87},\cite{Jensen91}, Valid time, bi-temporal \cite{Snodgrass84}(both valid and transaction time) or tri-temporal \cite{Nascimento95} (valid, transaction and decision time).

Fuzzy temporal models \cite{schockaert08} deal with time points \cite{Dubois89} or intervals \cite{Garrido2009} that are ill-known. Some fuzzy temporal models assume that the time stored in the database is an interval. The temporal interval is represented by two ill-known time points: $X$  an ill-known starting point and $Y$ an ill-known ending point. The interval $\left[X,Y\right]$ is not a fuzzy interval but an ill-known interval: it is a crisp interval but it is partially unknown which values are in this interval.
